A comprehensive approach to analyzing environmental data with non-detects

### 2024-06-07 Rmarkdown/README.Rmd
readme update

```{r figure-2, fig.cap="**Figure 2.** Titanium concentration time series representing biosolids collected at three locations (light lines). Model predictions are superimposed in bold, the shaded regions represent a 95% credible interval on the posterior mean, and non-detects are shown as vertical dashed lines extending to the detection limit. A single value beyond the plot limits is annotated."}
knitr::include_graphics(here("figures/figure-censored-response.png"))
```

@@

```{r figure-3, fig.cap="**Figure 3.** Cobalt concentrations as a function of cadmium concentrations in biosolids from three treatment facilities. Nondetect cadmium concentrations are represented as horizontal lines extending to the detection limit. A robust (Student t) linear model is superimposed in blue and the shaded region represents a 95% credible interval on the posterior mean. The equivalent non-robust model yields an extremely wide credible interval due to the unusually high cobalt concentration of 309 µg g^-1^. Coordinates outside the plotting limits are annotated in parentheses."}
knitr::include_graphics(here("figures/figure-censored-predictor.png"))
```

@@

```{r figure-4, fig.cap="**Figure 4. (a)** Pairwise Bayesian correlations among the elemental concentrations in the dataset, estimated using Student t and Gaussian likelihoods. **(b)** The robust model---fitted with Student t likelihoods---identifies more correlation than the non-robust model fitted with Gaussian likelihoods."}
knitr::include_graphics(here("figures/figure-correlation-matrix.png"))
```

@@

```{r figure-5, fig.cap="**Figure 5. (a)** The dataset projected onto the first two probabilistic principal components (*z* in equation (6)). Values appearing outside the extents of the plot are annotated in parentheses at the margins. **(b)** The first two principal axes; that is, the orthonormalized columns of the transformation matrix $W$."}
knitr::include_graphics(here("figures/figure-ppca.png"))
```

>>>>

```{r figure-2, fig.cap="**Figure 2.** Titanium concentration time series representing biosolids collected at three locations (light lines). Model predictions are superimposed in bold, the shaded regions represent a 95% credible interval on the posterior mean, and non-detects are shown as vertical dashed lines extending to the detection limit. A single value beyond the plot limits is annotated."}
knitr::include_graphics("https://github.com/bentrueman/censored-env-data-analysis/blob/main/figures/figure-censored-response.png")
```

@@

```{r figure-3, fig.cap="**Figure 3.** Cobalt concentrations as a function of cadmium concentrations in biosolids from three treatment facilities. Nondetect cadmium concentrations are represented as horizontal lines extending to the detection limit. A robust (Student t) linear model is superimposed in blue and the shaded region represents a 95% credible interval on the posterior mean. The equivalent non-robust model yields an extremely wide credible interval due to the unusually high cobalt concentration of 309 µg g^-1^. Coordinates outside the plotting limits are annotated in parentheses."}
knitr::include_graphics("https://github.com/bentrueman/censored-env-data-analysis/blob/main/figures/figure-censored-predictor.png")
```

@@

```{r figure-4, fig.cap="**Figure 4. (a)** Pairwise Bayesian correlations among the elemental concentrations in the dataset, estimated using Student t and Gaussian likelihoods. **(b)** The robust model---fitted with Student t likelihoods---identifies more correlation than the non-robust model fitted with Gaussian likelihoods."}
knitr::include_graphics("https://github.com/bentrueman/censored-env-data-analysis/blob/main/figures/figure-correlation-matrix.png")
```

@@

```{r figure-5, fig.cap="**Figure 5. (a)** The dataset projected onto the first two probabilistic principal components (*z* in equation (6)). Values appearing outside the extents of the plot are annotated in parentheses at the margins. **(b)** The first two principal axes; that is, the orthonormalized columns of the transformation matrix $W$."}
knitr::include_graphics("https://github.com/bentrueman/censored-env-data-analysis/blob/main/figures/figure-ppca.png")
```
